---
title: "FAIR Analysis"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
navbar:
- { title: "About OpenFAIR", href: "https://blog.opengroup.org/2017/01/24/what-is-open-fair", right }
runtime: shiny
params:
  model_directory: "~/workspace/risk-analysis-ui/model"
---

```{r setup, include=FALSE}
library(extrafont)
library(evaluator)
library(tidyverse)
library(flexdashboard)
library(ggplot2)
library(mc2d)
library(shiny)
library(scales)
library(viridis)
library(readr)
library(purrr)
library(future)
library(DT)
library(statip)

plan(multiprocess)

source("../R/risk_model.R", local=TRUE)
source("../R/risk_scenario.R", local=TRUE)
source("../R/risk_plot.R", local=TRUE)
source("../R/risk_matrix_plot.R", local=TRUE)
```

```{r core_functions, include=FALSE}
# determine the proper base font to use for graphs
basefont <- get_base_fontfamily()

model_directory <- params$model_directory

values <- reactiveValues()
values$iterations <- 1000
values$modelLoaded <- FALSE

observeEvent(input$loadSimResults, {
    showNotification("Loading FAIR results")
    values$results <- load_simulation_model(input$modelName)
    values$modelLoaded <- TRUE
    showNotification("Results Loaded")
})

observeEvent(input$runSim, {
    showNotification("Running FAIR analysis")
    model_results <- run_model_simulation(input$modelName, input$iterations)

    showNotification("Summarising results")
    values$results <- summarize_model_simulation(model_results)
    values$modelLoaded <- TRUE
    showNotification("Summarising results completed")
})
```

Domain Characteristics
========================================================================

Input Sidebar {.sidebar data-width=300}
------------------------------------------------------------------------

```{r model_inputs}
selectInput("modelName", h3("Select FAIR Analysis"), choices = get_model_list(model_directory))
actionButton("loadSimResults", "Load Analysis", width = "250px")
sliderInput("iterations", h3("Number of iterations"), min=100, max=100000, value=1000)
actionButton("runSim", "Run Analysis", width = "250px")
```

Row
------------------------------------------------------------------------

### Domains

```{r}
renderTable({
    if (values$modelLoaded) {
        domains <- values$results$model_results$model_data$domains

        select(domains, domain_id, domain) %>%
            rename("Asset ID" = domain_id,
                   "Asset" = domain)
    }
})
```

### Domain Capabilities

```{r}
renderTable({
    if (values$modelLoaded) {
        domains <- values$results$model_results$model_data$domains
        capabilities <- values$results$model_results$model_data$capabilities

        inner_join(capabilities, domains, by = "domain_id") %>%
            select(domain, capability_id, capability, diff) %>%
            rename("Asset" = domain,
                   "Capability ID" = capability_id,
                   "Capability" = capability,
                   "Difficulty" = diff)
    }
})
```

Row
------------------------------------------------------------------------

### Domain Threat Scenarios

```{r}
renderTable({
    if (values$modelLoaded) {
        domains <- values$results$model_results$model_data$domains
        scenarios <- values$results$model_results$model_data$qualitative_scenarios

        inner_join(scenarios, domains, by = "domain_id") %>%
            select(domain, scenario_id, scenario, tcomm, tef, tc, lm, controls) %>%
            rename("Asset" = domain,
                   "Scenario ID" = scenario_id,
                   "Scenario" = scenario,
                   "Threat Actor" = tcomm,
                   "Threat Frequency" = tef,
                   "Threat Capability" = tc,
                   "Loss Magnitude" = lm,
                   "Controls" = controls)
    }
})
```

Domain Risk Matrix
========================================================================

Row
------------------------------------------------------------------------

### Risk Matrix

```{r}
renderPlot({
    if (values$modelLoaded) {
        generate_risk_matrix(
            map_risk_matrix(
                summarize_domain_risk(
                    values$results$summarise_results$domain_summary
                )
            )
        )
    }
})
```

### Risk Matrix Values

```{r}
renderTable({
    if (values$modelLoaded) {
        map_risk_matrix(
            summarize_domain_risk(
                    values$results$summarise_results$domain_summary
            )
        ) %>%
            mutate(ale_var = scales::dollar(ale_var)) %>%
            select("ID" = ID,
                   "Asset" = domain,
                   "Value at Risk" = ale_var,
                   "Mean Loss Events" = mean_loss_events,
                   "Likelihood" = Likelihood,
                   "Impact" = Impact)

    }
})
```

The risk matrix maps the following values:

* __Impact__: 95% Value at Risk (Annual Loss Expected)
* __Likelihood: Mean loss events

Default Risk Ratings set in the Risk Matrix Plot are:

Impact  | Range
--------|------------
Low     | $0    - $2M
Medium  | >$2M  - $5M
High    | >$5M  - $15M
Serious | >$15M - $40M
Extreme | >$40M

Likelihood     | Range
---------------|------------
Rare           | 0.00 - 0.05
Unlikely       | 0.05 - 0.30
Possible       | 0.30 - 0.50
Likely         | 0.50 - 0.80
Almost Certain | 0.80 - 1.00

Domain Summary
========================================================================

Row
------------------------------------------------------------------------

### 95% Value at Risk {.value-box}

``` {r}
renderValueBox({
    if (values$modelLoaded) {
        iteration_summary <- values$results$summarise_results$iteration_summary

        agg_risk <- quantile(iteration_summary$ale_sum, 0.95)
        valueBox(format(agg_risk, nsmall = 2, big.mark = ","))
    }
})
```

### Expected Annual Loss Events {.value-box}

```{r}
renderValueBox({
    if (values$modelLoaded) {
        iteration_summary <- values$results$summarise_results$iteration_summary

        loss_events <- median(iteration_summary$loss_events)
        valueBox(format(loss_events, nsmall = 2))
    }
})
```

Row
------------------------------------------------------------------------

### Domain Summary Table

``` {r domain_summary_table}
renderTable({
    if (values$modelLoaded) {
        values$results$summarise_results$domain_summary %>%
            arrange(desc(ale_var)) %>%
            mutate(ale_min = scales::dollar(ale_min),
                   ale_median = scales::dollar(ale_median),
                   ale_mean = scales::dollar(ale_mean),
                   ale_max = scales::dollar(ale_max),
                   ale_sd = scales::dollar(ale_sd),
                   ale_var = scales::dollar(ale_var)) %>%
            select("ID" = domain_id,
                   "Asset" = domain,
                   "95% Value at Risk" = ale_var,
                   "Min ALE" = ale_min,
                   "Median ALE" = ale_median,
                   "Mean ALE" = ale_mean,
                   "Max ALE" = ale_max,
                   "Std Dev ALE" = ale_sd)
    }
})
```

Loss Ranges and Exceedance Curve
========================================================================

### Loss Ranges for Top Scenarios {.no-padding}

``` {r loss_across_scenarios}
renderPlot({
       if (values$modelLoaded) {
           simulation_results <- values$results$model_results$simulation_results
           if (nrow(simulation_results %>% unnest(results) %>% filter(sum(ale) != 0)) > 0) {
               plot_data <- cluster_scenario_loss(simulation_results)
               gg <- plot_loss_across_scenarios(plot_data)
               gg
           }
       }
})
```

### Loss Exceedance Curve for 80% Confidence

``` {r loss_exceedance_curve}
renderPlot({
    if (values$modelLoaded) {
        plot_loss_exceedance_curve(values$results$summarise_results$iteration_summary)
    }
})
```

Top Scenarios
========================================================================

### Top Threats

``` {r top_risk_scenarios}
renderTable({
       if (values$modelLoaded) {
           scenario_summary <- values$results$summarise_results$scenario_summary
           scenarios <- values$results$summarise_results$scenarios

           top_n(scenario_summary, 10, ale_var) %>%
               arrange(desc(ale_var)) %>%
               left_join(scenarios, by = c("scenario_id" = "scenario_id",
                                           "domain_id" = "domain_id")) %>%
               mutate(ale_var = scales::dollar(ale_var),
                      ale_median = scales::dollar(ale_median),
                      full_label = paste(domain_id, scenario_id, sep = " - ")) %>%
               select("ID" = full_label,
                      "Threat" = scenario_description,
                      "Median Annual Loss" = ale_median,
                      "Value at Risk" = ale_var)
       }
})

```

All Scenarios {data-orientation=rows}
========================================================================

Loss Distribution Scatterplot
------------------------------------------------------------------------

### Loss Distributions Across All Threat Scenarios

``` {r show_all_boxplot, fig.height=4}
shiny::renderPlot({
    if (values$modelLoaded) {
        simulation_data <- values$results$model_results$simulation_results %>% unnest(results)
        gg <- ggplot(simulation_data, aes(x = scenario_id, y = ale))
        gg <- gg + scale_y_continuous(labels = dollar_millions)
        gg <- gg + labs(x = "Risk Scenario", y = "Annual Loss")
        gg <- gg + stat_boxplot(geom = 'errorbar', width = 0.5)
        gg <- gg + geom_boxplot(fill = viridis(1), alpha = 1/3)
        gg <- gg + facet_grid(~ domain_id, scales = "free_x", space = "free_x", switch = "x")
        gg <- gg + theme_evaluator(base_family = basefont)
        gg <- gg + theme(panel.grid.major = element_blank())
        gg <- gg + theme(panel.grid.minor = element_blank())
        print(gg)
    }
})
```

All Scenarios Data Table
------------------------------------------------------------------------

### All Risk Scenarios

``` {r show_all_table}
DT::renderDataTable({
    if (values$modelLoaded) {
        summary_data <- values$results$summarise_results$scenario_summary
        dat <- mutate_at(summary_data, .funs = scales::dollar,
                         .vars = vars(starts_with("ale"), starts_with("sle"))) %>%
            mutate(loss_events_mean = comma(loss_events_mean)) %>%
            mutate(mean_tc_exceedance = percent(mean_tc_exceedance)) %>%
            mutate(mean_vuln = percent(mean_vuln)) %>%
            select(-c(control_descriptions, results))

        names(dat) <- names(dat) %>% stringr::str_replace("_", " ") %>%
            stringi::stri_trans_totitle()

        DT::datatable(dat,
                      rownames = FALSE,
                      options = list(
                          scrollX = TRUE,
                          scrollY = "300px",
                          fixedColumns = list(leftColumns = 2)),
                      extensions = c("Scroller", "FixedColumns"))
    }
})
```

Individual Risk Scenarios
========================================================================

Input Sidebar {.sidebar data-width=500}
------------------------------------------------------------------------

Select a specific risk scenario for detailed analysis.

``` {r inputs}
shiny::renderUI({
    if (values$modelLoaded) {
        selectInput(
            "input_scenario", h3("Select Risk Scenario"),
            get_scenarios(values$results$summarise_results$scenario_summary)
        )
    }
})
```

### Scenario Description

``` {r scenario_details}
shiny::renderText({
    if (values$modelLoaded) {
        get_scenario_description(
            input$input_scenario,
            values$results$summarise_results$scenarios
        )
    }
})
```

### Threat Profile

``` {r threat_profile}
shiny::renderText({
    if (values$modelLoaded) {
        paste(
            "Community:",
            get_threat_actor(
                input$input_scenario,
                values$results$summarise_results$scenarios
            )
        )
    }
})

shiny::renderTable({
    if (values$modelLoaded) {
        get_threat_table(
            input$input_scenario,
            values$results$summarise_results$scenarios
        )
    }
},
include.rownames = FALSE, width = 500)
```

#### Controls

``` {r controls}
shiny::renderTable({
    if (values$modelLoaded) {
        get_control_table(
            input$input_scenario,
            value$results$summarise_results$scenarios,
            values$results$model_results$model_data$capabilities
        )
    }
}, include.rownames = FALSE, width = 500)
```

#### Loss Magnitude

``` {r loss_magnitude}
shiny::renderTable({
    if (values$modelLoaded) {
        get_loss_distribution_table(
            input$input_scenario,
            values$results$summarise_results$scenarios
        )
    }
}, include.rownames = FALSE, width = 500)
```

Plot Display {data-width=450}
------------------------------------------------------------------------

### Loss Histogram and Density Distribution

``` {r show_densityplot}
shiny::renderPlot({
    if (values$modelLoaded) {
        plot_scenario(
            input$input_scenario,
            values$results$model_results$simulation_results
        )
    }
})
```

Main Display {data-width=450}
------------------------------------------------------------------------

### Value at Risk

``` {r var_values}
flexdashboard::renderValueBox({
    if (values$modelLoaded) {
        scenario_data <- values$results$model_results$simulation_results %>%
            unnest(results) %>%
            filter(scenario_id == get_scenario_id(input$input_scenario))

        dat <- quantile(scenario_data$ale, 0.95, na.rm = TRUE)
        if (is.na(dat)) dat <- 0

        risk_tolerances <- values$results$summarise_results$risk_tolerances
        flexdashboard::valueBox(
                           dollar(dat),
                           caption = "95% Value at Risk",
                           icon = "fa-pencil",
                           color = case_when(
                               dat >= risk_tolerances[risk_tolerances$level == "high",]$amount ~ "High",
                               dat >= risk_tolerances[risk_tolerances$level == "medium",]$amount ~ "Medium",
                               TRUE ~ "success"
                           )
                       )
    }
})
```

### Vulnerability

``` {r vuln_value}
flexdashboard::renderValueBox({
    if (values$modelLoaded) {
        sid <- get_scenario_id(input$input_scenario)
        dat <- values$results$summarise_results$scenario_summary %>%
            filter(scenario_id == sid) %>% pull(mean_vuln)
        if (is.na(dat)) dat <- 0

        flexdashboard::valueBox(
                           percent(dat),
                           caption = "Vulnerability",
                           icon = "ion-nuclear",
                           color = ifelse(
                               dat >= .75, "danger",
                               ifelse(
                                   dat >= .50, "warning", "success")))
    }
})

```

Detailed Display {data-width=400}
------------------------------------------------------------------------

### Summary Data

``` {r show_summary}
shiny::renderTable({
    if (values$modelLoaded) {
        scenario_id <- get_scenario_id(input$input_scenario)
        get_summary_table(
            scenario_id,
            values$results$summarise_results$scenario_summary
        )
    }
}, include.rownames = FALSE)
```

### Loss Table

``` {r show_loss_table}
shiny::renderTable({
    if (values$modelLoaded) {
        scenario_id <- get_scenario_id(input$input_scenario)
        get_loss_table(
            scenario_id,
            values$results$model_results$simulation_results
        )
    }
}, include.rownames = FALSE)
```
